Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-11 analysis/paper/paper.Rmd
All of the code for dorsal cortext visualization is present. Debugging likily needed. Will write analysis soon.

<!--(10 Feb 2022) QH: Just putting all of the code and writing here. Not going to worry about formatting for now -->
```{r}
library(tidyverse)

@@

>>>>

<!--(10 Feb 2022) QH: Just putting all of the code and writing here. Not going to worry about formatting for now -->
<!--(10 Feb 2022) QH: On a secondary note, I managed to cause an error with docker in record time. We will need to fix that later-->
<!--(10 Feb 2022) QH: Lastly, I'm going to do my best to get the code working tonight. If that fails, I will still write up my interpretation using prior images of the visualization-->

```{r}
library(tidyverse)

@@

```
```{r}
# here we import the CSV file of caliper measurements, then compute on the
# measurements to generate coordinates for a shape outline

library(tidyverse)

# import
ma_flakes_tr <- read_csv(here::here("data/ma_flakes_tr.csv"))

# custom function is from here, we have a local version in 999-functions.R
# so we can work offline if we need to
# https://gist.github.com/benmarwick/fac5754131c1fcc14d32b1658215f0e3

source(here::here("code/999-functions.R"))

polys <- polygon_shape_by_variables(data = ma_flakes_tr,       # our data frame
                                    x = 'width_at_0.50_length',                # col for coord for x-axis of poly centers
                                    y = 'max_dimension',       # col for coord for y-axis of poly centers

                                    sf = 10,    # scale factor
                                    top_horizontal_measurement =    'platform_width', # cols to use to compute poly verts
                                    main_vertical_measurement =     'percussion_length',
                                    upper_horizontal_measurement =  'width_at_0.25_length',
                                    middle_horizontal_measurement = 'width_at_0.50_length',
                                    bottom_horizontal_measurement = 'width_at_0.75_length')

# take a look to ensure we are on the right track
p <- ggplot() +
  geom_polygon(data=polys,
               aes(x=x,
                   y=y,
                   group = fill),
               colour="black",
               alpha = 0.5) +
  coord_equal() +
  theme_bw()
p

# make ready to convert to TPS format (thin plate spline)
polys_lmk <-
polys %>%
  group_by(fill) %>%
  mutate(landmark.number = row_number(fill),
         specimen.ids  = fill) %>%
  ungroup() %>%
  select(-fill)

# export as TPS file
create_tps(polys_lmk,
           here::here("data/landmarks.tps"))

```
```{r}
ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
  mutate(dorsal_cortext_group = as.factor(
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 50) ~ "Secondary",
             between(dorsal_cortex_perc, 51, 100) ~ "Primary"
           ))) %>% 
 mutate(mass_group = as.factor(test_result_mass$cluster))
# plot mass groups
ggplot(ma_flakes_tr_with_groups)  +
  aes(mass,
      fill = mass_group) +
  geom_histogram() +
  scale_fill_viridis_d(name = "Mass\ncluster") +
  xlab("Mass (g)") +
  theme_minimal(base_size = 14) +
  theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
        plot.background = element_rect(fill='white',
                                       colour = "white"))
